---
title: "Phase I: Automatic Water Classification - Statistical Analysis"
output: html_notebook
---

Import required packages.

```{r}
require(agricolae)
```

Read the results from the confusion images and join them in a single data frame.

```{r}
cm_a = read.csv("../data/phase-I/cm_alto_lindoso.csv")
cm_b = read.csv("../data/phase-I/cm_bubal.csv")
cm_c = read.csv("../data/phase-I/cm_canelles.csv")
cm_g = read.csv("../data/phase-I/cm_grado.csv")

cm_a$Reservoir = rep("Alto-Lindoso",nrow(cm_a))
cm_b$Reservoir = rep("Bubal",nrow(cm_b))
cm_c$Reservoir = rep("Canelles",nrow(cm_c))
cm_g$Reservoir = rep("Grado",nrow(cm_g))

cm = rbind(cm_a,cm_b,cm_c,cm_g)
```

Compute the MCC.

```{r}
cm$TP = as.double(cm$TP)
cm$FP = as.double(cm$FP)
cm$FN = as.double(cm$FN)
cm$TN = as.double(cm$TN)

cm$MCC = ((cm$TP*cm$TN)-(cm$FP*cm$FN))/sqrt((cm$TP+cm$FP)*(cm$TP+cm$FN)*(cm$TN+cm$FP)*(cm$TN+cm$FN))
```

Convert Grid Type (G), Seed Spacing (S), number of clusters (K) and training size (T) to factors for analysis.

```{r}
cm$GridType = as.factor(cm$GridType)
cm$k = as.factor(cm$k)
cm$SeedSpacing = as.factor(cm$SeedSpacing)
cm$TrainingPrSuperpixels = as.factor(cm$TrainingPrSuperpixels)
cm$Reservoir = as.factor(cm$Reservoir)
```

## MCC Analysis

First, the ANOVA is performed.

```{r}
fit = aov(MCC ~ GridType*k*SeedSpacing*TrainingPrSuperpixels,cm)
summary(fit)
```

Since just G, K and S were significant, LSD was done on these factors.

```{r}
LSD_G = LSD.test(fit,c("GridType"))
LSD_K = LSD.test(fit,c("k"))
LSD_S = LSD.test(fit,c("SeedSpacing"))

plot(LSD_G,variation = "SE",main = "Grid Type")
plot(LSD_K,variation = "SE",main = "Number of Clusters")
plot(LSD_S,variation = "SE",main = "Seed Spacing")
```

## Sensitivity Analysis

Sensitivity did not show significant differences. Therefore, LSD was not performed.

```{r}
fit = aov(Sensitivity ~ GridType*k*SeedSpacing*TrainingPrSuperpixels,cm)
summary(fit)
```

## Precision Analysis

First, the ANOVA is performed.

```{r}
fit = aov(Precision ~ GridType*k*SeedSpacing*TrainingPrSuperpixels,cm)
summary(fit)
```

Since only K and S were significant, LSD was done on these factors.

```{r}
LSD_K = LSD.test(fit,c("k"))
LSD_S = LSD.test(fit,c("SeedSpacing"))

plot(LSD_K,variation = "SE",main = "Number of Clusters")
plot(LSD_S,variation = "SE",main = "Seed Spacing")
```

## Time Analysis

First, the ANOVA is performed.

```{r}
fit = aov(Time ~ GridType*k*SeedSpacing*TrainingPrSuperpixels,cm)
summary(fit)
```

Since only K, S and T were significant, LSD was done on these factors.

```{r}
LSD_K = LSD.test(fit,c("k"))
LSD_S = LSD.test(fit,c("SeedSpacing"))
LSD_T = LSD.test(fit,c("TrainingPrSuperpixels"))

plot(LSD_K,variation = "SE",main = "Number of Clusters")
plot(LSD_S,variation = "SE",main = "Seed Spacing")
plot(LSD_T,variation = "SE",main = "Training Size")
```

