---
title: "Phase II: Satellite Derived Bathymetry - Statistical Analysis"
output: html_notebook
---

Import required packages.

```{r}
require(agricolae)
require(tidyr)
```

## Random Forest (RF)

Read the results from the grid search conducted in sklearn.

```{r}
cvrf.broader = read.csv("../data/phase-II/results/RF/gridsearchcv-results-rf-broader.csv")
cvrf.narrower = read.csv("../data/phase-II/results/RF/gridsearchcv-results-rf-narrower.csv")
```

### Broader Tuning

First, we organize the cross-validation results.

```{r}
cvrf.broader = cvrf.broader %>% gather("split_test",
                                       "RMSE",
                                       split0_test_score,
                                       split1_test_score,
                                       split2_test_score)

cvrf.broader = cvrf.broader[,c(5,6,10:11)]
names(cvrf.broader)[1:2] = c("Maximum Input Features","Estimators")
cvrf.broader$RMSE = cvrf.broader$RMSE*-1
```

Convert factors.

```{r}
cvrf.broader$`Maximum Input Features` = as.factor(cvrf.broader$`Maximum Input Features`)
cvrf.broader$Estimators = as.factor(cvrf.broader$Estimators)
```

The ANOVA is fitted.

```{r}
fit = aov(RMSE ~ `Maximum Input Features`*Estimators,cvrf.broader)
summary(fit)
```

Check for LSD significances.

```{r}
LSD_M = LSD.test(fit,c("Maximum Input Features"))
LSD_E = LSD.test(fit,c("Estimators"))

plot(LSD_M,variation = "SE",main = "Maximum Input Features")
plot(LSD_E,variation = "SE",main = "Estimators")
```

In this case, the RMSE using a maximum input features $\sqrt{n}$ is significantly lower than using all the input features $n$. There are no differences in estimators.

### Narrower Tuning

Organize the cross-validation results for the narrower tuning.

```{r}
cvrf.narrower = cvrf.narrower %>% gather("split_test",
                                         "RMSE",
                                         split0_test_score,
                                         split1_test_score,
                                         split2_test_score,
                                         split3_test_score,
                                         split4_test_score)

cvrf.narrower = cvrf.narrower[,c(5,9:10)]
names(cvrf.narrower)[1] = "Estimators"
cvrf.narrower$RMSE = cvrf.narrower$RMSE*-1
```

Convert the factor.

```{r}
cvrf.narrower$Estimators = as.factor(cvrf.narrower$Estimators)
```

Fit the ANOVA.

```{r}
fit = aov(RMSE ~ Estimators,cvrf.narrower)
summary(fit)
```

Check for differences.

```{r}
LSD_E = LSD.test(fit,c("Estimators"))

plot(LSD_E,variation = "SE",main = "Estimators")
```

Sinificant differences were not found. The best number of estimators was selected as the one with the least time and a slightly better RMSE (mean and std): 20 estimators.

## Gradient Boosting (GB)

Read the cross-validation results.

```{r}
gscv.gb = read.csv("../data/phase-II/results/GB/gridsearchcv-results-gb.csv")
```

Organize the results.

```{r}
gscv.gb = gscv.gb %>% gather("split_test",
                             "RMSE",
                             split0_test_score,
                             split1_test_score,
                             split2_test_score,
                             split3_test_score,
                             split4_test_score)

gscv.gb = gscv.gb[,c(5,9,10)]
names(gscv.gb)[1] = "Maximum Depth"
gscv.gb$RMSE = gscv.gb$RMSE*-1
```

Covert to factor.

```{r}
gscv.gb$`Maximum Depth` = as.factor(gscv.gb$`Maximum Depth`)
```

Fit the ANOVA. There ar no significant differences.

```{r}
fit = aov(RMSE ~ `Maximum Depth`,gscv.gb)
summary(fit)
```

Check the LSD test.

```{r}
LSD_D = LSD.test(fit,c("Maximum Depth"))

plot(LSD_D,variation = "SE",main = "Maximum Depth")
```

No significant differences were found. The maximum depth of 20 levels was selected as the value with the least consumed time.
